Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-07 demystify.tex
updates

\paragraph{You aim too high}  This is a very common reason: you have applied to schools that are too high for your profile. While being ambitious is good, you should understand how PhD admission works (e.g., by reading this handbook and realizing things such as having a good GPA doesn't mean much) and be realistic!

@@

% I first skim the summary for school, GPA, standard tests and look for red flags like low GPA or test scores that do not meet the minimum requirements. Then I scan transcripts for low/failing grades on CS and related courses.  For these I make comments such as ``- unknown international school with good GPA, too many low grades on CS and related courses" or ``+ very good GPA from top school XYZ". I do not look at test details as the summary already gives the main scores.

>>>>

\paragraph{You aim too high}  This is a very common reason: you have applied to schools that are too high for your profile. While being ambitious is good, you should understand how PhD admission works (e.g., by reading this document and realizing things such as having a good GPA doesn't mean much to top programs) and be realistic!

@@

% I first skim the summary for school, GPA, standard tests and look for red flags like low GPA or test scores that do not meet the minimum requirements set by the university. Then I scan transcripts for low/failing grades on CS and related courses.  For these I make comments such as ``- unknown international school with good GPA, too many low grades on CS and related courses" or ``+ very good GPA from top school XYZ". I do not look at test details as the summary already gives the main scores.
